Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-02-12 batchdedup/arch.tex
paper revision. also major figure refactoring.

We consider deduplication in two levels. The first level
uses coarse-grain segment  dirty bits for version-based detection~\cite{Clements2009,Vrable2009}.
% to identify difference from the previous snapshot to the current snapshot.  
%That  can be accomplished efficiently and inexpensively in the OS level.
%We use a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
Our experiment with Alibaba's production dataset shows that over 70 percentage of 
duplicates can be detected using segment dirty bits when the segment size is 2M bytes.  
This setting requires the virtual disk driver to maintain segment dirty bits,
which has a negligible space cost (1 bit per 2 MB). In the second level of deduplication, content blocks of dirty segments 
are compared with the fingerprints of unique  blocks from previous snapshots.
Our key strategies are explained as follows.
\begin{itemize}

\item {\bf Separation of duplicate detection and data backup.}
%Request accumulation and partition-based deduplication.}
The second level detection requires a global comparison of fingerprints.
% of stored chunks with the new chunks scanned during the backup process. 
%Bloom filters and caching allows some of content 
%fingerprints to be stored on the cheap disks~\cite{bottleneck08}. Such an optimization is good 
%for inline deduplication where chunks scanned need to be determined to be duplicate or not instantly without 
%waiting while  it memory consumption is still significant in competing with stand virtual 
%machine activities.  
Our approach is to perform duplicate detection first before actual data backup.
That requires a prescanning of  dirty VM segments, which
%  and after that, real backup  for those non-duplicates is conducted. 
does incur an extra  round of VM reading.
% while avoiding inline deduplication and leading to a much smaller resource requirement.  
During VM prescanning, detection requests are accumulated.
Aggregated deduplicate requests can be processed partition by partition. 
%We also accumulate the delete requests and perform them partition by partitions. 
Since each partition corresponds to a small portion of global index, 
memory cost to process detection requests within a partition is small.
%the cost to process detection requests within a partition is significantly smaller than processing all 
%the requests globally.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/batch_arch.pdf}
\caption{Overall architecture of parallel VM snapshot deduplication}
\label{fig:snapshot}
\end{figure}
%\subsection{Snapshot Representation}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{images/Stage1.pdf}
\caption{Processing flow of Stage 1.}
\label{fig:stage1}
\end{figure}

%\subsection{Processing flow and resource usage}
%The data flow of our multi-stage duplicate detection is depicted in Figure~\ref{fig:flow}. 
%\begin{itemize}
%\item
In Stage 1a, each machine independently reads  
%$v/k$  
VM images that need a backup
and forms duplicate  detection requests. 
%For those dirty segments,
%segments that have been modified since last backup indicated by dirty bits,  
The system divides  each dirty segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends a request to a proper machine, and accumulates  
received requests into a partition on the local temporary disk storage. 
The partition mapping uses a hash function applied to the content fingerprint. 
Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
$q$ partitions of global index and it accumulates corresponding requests on the disk. 
There are two options to allocate buffers at each machine. 
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since a content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine allocates $p$ send buffers to deliver requests to $p$ machines; it allocates 
$p$ receive buffers to collect requests  from other machines.
Then the system copies requests from each of $p$ receive buffers to  $q$ local request buffers,
and outputs each request buffer to one of the request partitions on the disk
when this request buffer becomes full.  Option 2, which is  depicted in Figure~\ref{fig:flow},
is much more efficient than Option 1 because $2p+q$ is much smaller than
$p\times q$, except for the very small  values. 
As a result, each buffer in Option 2 has a bigger size to accumulate requests and that means
less disk seek overhead.

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{images/Stage2.pdf}
\caption{Processing flow of Stage 2.}
\label{fig:stage2}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{images/Stage3.pdf}
\caption{Processing flow of Stage 3.}
\label{fig:stage3}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{images/Stage4.pdf}
\caption{Processing flow of Stage 4.}
\label{fig:stage4}
\end{figure}

>>>>

We consider deduplication in two levels. The first level
uses coarse-grain segment  dirty bits for version-based detection~\cite{Clements2009,Vrable2009}.
% to identify difference from the previous snapshot to the current snapshot.  
%That  can be accomplished efficiently and inexpensively in the OS level.
%We use a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
Our experiments with Alibaba's production dataset shows that over 70 percent of 
duplicates can be detected using segment dirty bits when the segment size is 2M bytes.  
This setting requires the virtual disk driver to maintain segment dirty bits,
which has a negligible space cost (1 bit per 2 MB). In the second level of deduplication, content blocks of dirty segments 
are compared with the fingerprints of unique  blocks from previous snapshots.
Our key strategies are explained as follows.
\begin{itemize}

\item {\bf Separation of duplicate detection and data backup.}
%Request accumulation and partition-based deduplication.}
The second level detection requires a global comparison of fingerprints.
% of stored chunks with the new chunks scanned during the backup process. 
%Bloom filters and caching allows some of content 
%fingerprints to be stored on the cheap disks~\cite{bottleneck08}. Such an optimization is good 
%for inline deduplication where chunks scanned need to be determined to be duplicate or not instantly without 
%waiting while  it memory consumption is still significant in competing with stand virtual 
%machine activities.  
Our approach is to perform duplicate detection first before actual data backup.
This requires a prescanning of  dirty VM segments, which
%  and after that, real backup  for those non-duplicates is conducted. 
does incur an extra  round of VM reading.
% while avoiding inline deduplication and leading to a much smaller resource requirement.  
During VM prescanning, detection requests are accumulated.
Aggregated deduplicate requests can be processed partition by partition. 
%We also accumulate the delete requests and perform them partition by partitions. 
Since each partition corresponds to a small portion of global index, 
memory cost to process detection requests within a partition is small and can
be handled in memory.
%the cost to process detection requests within a partition is significantly smaller than processing all 
%the requests globally.

@@

\begin{figure}
\centering
%\includegraphics[width=0.5\textwidth]{batch_arch}
%this is an alternate version of the figure done completely in latex
\input{figures/batch_arch}
\caption{Overall architecture of parallel VM snapshot deduplication}
\label{fig:snapshot}
\end{figure}
%\subsection{Snapshot Representation}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{Stage1}
\caption{Processing flow of Stage 1.}
\label{fig:stage1}
\end{figure}

%\subsection{Processing flow and resource usage}
%The data flow of our multi-stage duplicate detection is depicted in Figure~\ref{fig:flow}. 
%\begin{itemize}
%\item
In Stage 1a, each machine independently reads  
%$v/k$  
VM images that need a backup
and forms duplicate  detection requests. 
%For those dirty segments,
%segments that have been modified since last backup indicated by dirty bits,  
The system divides  each dirty segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends a request to a proper machine, and accumulates  
received requests into a partition on the local temporary disk storage. 
The partition mapping uses a hash function applied to the content fingerprint. 
Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
$q$ partitions of global index and it accumulates corresponding requests on the disk. 
There are two options to allocate buffers at each machine. 
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since a content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine allocates $p$ send buffers to deliver requests to $p$ machines; it allocates 
$p$ receive buffers to collect requests  from other machines.
Then the system copies requests from each of $p$ receive buffers to  $q$ local request buffers,
and outputs each request buffer to one of the request partitions on the disk
when this request buffer becomes full.  Option 2, which is  depicted in Figure~\ref{fig:stage1},
is much more efficient than Option 1 because $2p+q$ is much smaller than
$p\times q$, except for the very small  values. 
As a result, each buffer in Option 2 has a bigger size to accumulate requests and that means
less disk seek overhead.

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{Stage2}
\caption{Processing flow of Stage 2.}
\label{fig:stage2}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{Stage3}
\caption{Processing flow of Stage 3.}
\label{fig:stage3}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{Stage4}
\caption{Processing flow of Stage 4.}
\label{fig:stage4}
\end{figure}

### 2014-02-12 batchdedup/background.tex
paper revision. also major figure refactoring.

At a cloud cluster node providing access to multiple virtual machines, each
instance of a guest operating system runs on a virtual machine (VM), accessing
virtual hard disks represented as virtual disk image files in the host
operating system. For VM snapshot backups, file-level semantics are normally
not provided, and snapshot operations take place at the virtual device driver
level.  This meands no fine-grained file system metadata can be used to
determine the changed data.

@@

Another issue is the sheer size of the backups. to maintain mutiple daily
uncompressed snapshots of each VM would be very expensive, even though
most of the data remains the same from day to day, and even between VMs common
software packages and operating systems mean that the amount of unique data is
much smaller. Backup systems have been developed to use content fingerprints to
identify duplicate content~\cite{venti02,Rhea2008}. Offline deduplication is
used in~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks
during idle time.  Several techniques have been proposed to speedup searching
of duplicate fingerprints. For example, the data domain method
~\cite{bottleneck08} uses  an in-memory Bloom filter and a prefetching cache
for data blocks  which may be accessed.  An improvement to this work with
parallelization is in ~\cite{MAD210,DEBAR}.  As discussed in
Section~\ref{sect:intro}, there is no dedicated resource for deduplication in
our targeted setting and low memory usage is required so that the resource
impact to other cloud services is minimized. Approximation techniques which
reduce the memory requirement at the expense of deduplication efficiency are
studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}.  In comparison, this
paper focuses on full deduplication without approximation

>>>>

At a cloud cluster node providing access to multiple virtual machines, each
instance of a guest operating system runs on a virtual machine (VM), accessing
virtual hard disks represented as virtual disk image files in the host
operating system. For VM snapshot backups, file-level semantics are normally
not provided, and snapshot operations take place at the virtual device driver
level.  This means no fine-grained file system metadata can be used to
determine the changed data.

@@

Another issue is the sheer size of the backups. to maintain mutiple daily
uncompressed snapshots of each VM would be very expensive, even though
most of the data remains the same from day to day, and even between VMs common
software packages and operating systems mean that the amount of unique data is
much smaller. Backup systems have been developed to use content fingerprints to
identify duplicate content~\cite{venti02,Rhea2008}. Offline deduplication is
used in~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks
during idle time.  Several techniques have been proposed to speedup searching
of duplicate fingerprints. For example, the data domain method
~\cite{bottleneck08} uses  an in-memory Bloom filter and a prefetching cache
for data blocks  which may be accessed.  An improvement to this work with
parallelization is in ~\cite{MAD210,DEBAR}.  As discussed in
Section~\ref{sect:intro}, there is no dedicated resource for deduplication in
our targeted setting and low memory usage is required so that the resource
impact to other cloud services is minimized. Approximation techniques which
reduce the memory requirement at the expense of deduplication efficiency are
studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}.  In comparison, this
paper focuses on full deduplication without approximation.

### 2014-02-12 batchdedup/eval.tex
paper revision. also major figure refactoring.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{mem_time.pdf}
\caption{ Parallel time when memory limit varies.}
\label{fig:memory}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{mem_time}
\caption{ Parallel time when memory limit varies.}
\label{fig:memory}
\end{figure}

\comments{
alternate version of fig:memory done all in pgfplots
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            ybar stacked,
            width=0.85\columnwidth,
            cycle list name=mfill,
            bar width=0.70cm,
            style=very thin,
            symbolic x coords={35M,45M,55M,65M,95M,190M},
            %xlabel={Memory Usage},
            ylabel={Time (hours)},
            %extra y ticks={4.5,5.5,6.5}, %to add extra ticks
            xtick=data, %without this the symbolic coords may be repeated as filler
            enlarge x limits=0.15, %used to push plots towards center
            ymin=0,
            %ymax=4.,
            ytick={0,0.5,1,...,4},
            %{/pgf/number format/.cd,fixed,precision=2},
            ymajorgrids,
            grid style=densely dotted,
            major x tick style=transparent,
            tick label style={font=\scriptsize\mathversion{sans}\sffamily},
            label style={font=\footnotesize\sf},
            legend pos=south east,
            reverse legend,
            area legend,
            legend cell align=right,
            legend style={
                %    at={(0.5,-0.2)},
                %anchor=north,
                font=\scriptsize\sf,
                %draw=none,
            },
            ]
            \addplot table[header=false,x index=0,y index=2] {figures/mem_time_new.data};
            \addlegendentry{Stage 1}
            \addplot table[header=false,x index=0,y index=3] {figures/mem_time_new.data};
            \addlegendentry{Stage 2}
            \addplot table[header=false,x index=0,y index=4] {figures/mem_time_new.data};
            \addlegendentry{Stage 3}
            %\legend{Data read/write,Network cost, Index access/lookup}
            \end{axis}
    \end{tikzpicture}
    \caption{Parallel time when memory limit varies}
  \label{fig:memory}
\end{figure}
}

### 2014-02-12 batchdedup/intro.tex
paper revision. also major figure refactoring.

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host
%tens of thousands of  virtual machines(VM) created for various active users.
Periodic  archiving of virtual machine (VM) snapshots is important 
for long-term data  retention and fault recovery. 
%in case of machine failures.  
For example, daily backup of VM images  is conducted automatically 
at Alibaba which provides the largest public cloud service in China.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
identifies redundant content duplicates among snapshots.  
One architectural approach is to attach  a separate backup system with deduplication support such as ones
from  EMC~\cite{EMC} or NetApp{NetApp}
to the cloud cluster, and  the snaphosts of every virtual machine is   periodically transferred to
the attached backup system.  Such a dedicated backup  configuration can be expensive, 
considering that significant networking  and computing resource  is required 
to transfer undeduplicatd data and conduct signature comparison. 
Our work is targeted applications where data processing and archiving  can be conducted
in an inexpensive commodity storage cluster using the  Google file system or Hadoop~\cite{googlefs03}
and such a storage cluster is non-dedicated, shared with other services running in the entire cluster.
Resource sharing is common especially in the cloud where many computing and storage
services are collocated in the same physical machines.

With  resource sharing with other services as an assumption, we are motivated to develop a 
low-profile backup solution with deduplication. 
Deduplication is a major

@@

Among the three factors - time, cost and deduplication efficiency, one of them has to be compromised for the other two. For instance, if we were building a deduplication system that has a high rate of duplication detection and has a very fast response time, 
it would need a lot of memory to hold fingerprint index and cache.  This leads to a compromise on cost. 
Our objective is to lower the cost incurred while sustaining the highest de-duplication ratio
and  a sufficient throughput in dealing with a large number of VM images.% This business model partially  resembles that of Amazon Glacier.

>>>>

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host
%tens of thousands of  virtual machines(VM) created for various active users.
Periodic  archiving of virtual machine (VM) snapshots is important 
for long-term data  retention and fault recovery. 
%in case of machine failures.  
For example, daily backup of VM images  is conducted automatically 
at Alibaba which provides the largest public cloud service in China.
The cost of frequent backup of VM snapshots is  high because of the huge storage demand.
This issue has been addressed by   storage data deduplication ~\cite{venti02,bottleneck08} that
identifies redundant content duplicates among snapshots.  
One architectural approach is to attach  a separate backup system with deduplication support such as ones
from  EMC~\cite{EMC} or NetApp{NetApp}
to the cloud cluster, and  the snaphosts of every virtual machine is   periodically transferred to
the attached backup system.  Such a dedicated backup  configuration can be expensive, 
considering that significant networking  and computing resource  is required 
to transfer undeduplicatd data and conduct signature comparison. 
Our work is targeted applications where data processing and archiving  can be conducted
in an inexpensive commodity storage cluster using a distributed file system
such as the Google file system or Hadoop~\cite{googlefs03,hdfs10}.
Resource sharing is common, especially in the cloud where many computing and storage
services are collocated in the same physical machines, so we 
expect the storage cluster to be non-dedicated.

With  resource sharing with other services as an assumption, we are motivated to develop a 
low-profile backup solution with deduplication. 
%Deduplication is a major

@@

%Among the three factors - time, cost and deduplication efficiency, one of them
%has to be compromised for the other two. For instance, if we were building a
%deduplication system that has a high rate of duplication detection and has a
%very fast response time, 
%it would need a lot of memory to hold fingerprint index and cache.  This leads to a compromise on cost. 
%Our objective is to lower the cost incurred while sustaining the highest de-duplication ratio
%and  a sufficient throughput in dealing with a large number of VM images.% This business model partially  resembles that of Amazon Glacier.

Among the three factors - time, cost, and deduplication efficiency, our main
objective is low cost, so as to not significantly impact primary services. By
sacrificing memory a faster deduplication system
can be built, but then machines must be dedicated to backup, which goes
against the converged architecture model that we are supporting. For daily
backup jobs, it is ok if the job takes 2-3 hours, as long as the resource
usage is minimal and it can be finished during lower usage hours of the day.

### 2014-02-12 batchdedup/main.tex
Additional cluster histogram added
paper revision. also major figure refactoring.

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{listings}
%\lstset{language=C}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
%\makeatletter
%\def\url@leostyle{%
%  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
%\makeatother
%% Now actually use the newly defined style.
%\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}

\usepackage{pgfplots}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

%pgfplots setup
\pgfplotsset{every axis/.append style={
	very thick,
	tick style={thick}}}
\pgfplotsset{
        every mark/.append style={solid}
}
%this is my preferred default cycle list for pgfplots.
\pgfplotscreateplotcyclelist{mcolor}{%
    {blue,every mark/.append style={fill=blue},mark=*},
    {red,every mark/.append style={fill=red},mark=square*},
    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=3},
    {black,every mark/.append style={fill=black},mark=diamond*,mark size=3},
    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3},
    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=2.7},
    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=2.7},
    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3}}

\pgfplotscreateplotcyclelist{mmark*}{
    {mark=*},
    {mark=square*},
    {mark=triangle*,mark size=2.7},
    {mark=diamond*,mark size=2.7},
    {mark=pentagon*,mark size=2.5},
    {mark=star,mark size=3},
    {mark=asterisk,mark size=3},
    {mark=+,mark size=3},
    {mark=Mercedes star,mark size=3}}

\pgfplotscreateplotcyclelist{mline}{
    {solid,blue,every mark/.append style={fill=blue}},
    {densely dashed,red,every mark/.append style={fill=red}},
    {densely dotted,brown,every mark/.append style={fill=brown}},
    {loosely dotted,black,every mark/.append style={fill=black}},
    {loosely dashed,green!60!black,every mark/.append style={fill=green!60!black}},
    {densely dashdotted,magenta!90!black,every mark/.append style={fill=magenta!90!black}},
    {densely dashdotdotted,teal,every mark/.append style={fill=teal}},
    {loosely dashdotted,orange,every mark/.append style={fill=orange}},
    {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}

>>>>

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[usenames]{xcolor}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{sansmath}
%\usepackage{listings}
\usepackage[]{algorithm2e}
%\lstset{language=C}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
%\makeatletter
%\def\url@leostyle{%
%  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
%\makeatother
%% Now actually use the newly defined style.
%\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}

\usepackage{subfigure}
%\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{pgfplots}
\pgfplotsset{compat=1.8}
\DeclareGraphicsExtensions{.pdf}
\graphicspath{ {./images/}{./figures/} }

%pgfplots setup
\usetikzlibrary{patterns}
\tikzset{ %I believe this sets the defaults, but I am not sure
    hatch distance/.store in=\hatchdistance,
    hatch distance=10pt,
    hatch thickness/.store in=\hatchthickness,
    hatch thickness=2pt
}
\pgfplotsset{
    %You are supposed to use append style rather than just setting
    %parameters globally so they are easier to override to special cases
    %thickness options:thin,ultra thin,very thin,semithick,thick,very thick
    every axis/.append style={
        very thick,
        tick style={thick},
        tick label style={font=\small\mathversion{sans}\sffamily},
        label style={font=\small\sffamily},
        font={\small\sffamily},
        %mark size=1.0
    },
    every legend/.append style={font={\small\mathversion{sans}\sffamily}}
}
\pgfplotsset{
        every mark/.append style={solid}
}

%this is my preferred default cycle list for pgfplots.
\pgfplotscreateplotcyclelist{mcolor}{%
    {blue,every mark/.append style={fill=blue},mark=*},
    {red,every mark/.append style={fill=red},mark=square*},
    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=3},
    {black,every mark/.append style={fill=black},mark=diamond*,mark size=3},
    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3},
    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=2.7},
    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=2.7},
    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3}}

%uses just line styles instead of marks to differentiate
\pgfplotscreateplotcyclelist{mline}{
    {solid,blue,every mark/.append style={fill=blue}},
    {densely dashed,red,every mark/.append style={fill=red}},
    {densely dotted,brown,every mark/.append style={fill=brown}},
    {loosely dotted,black,every mark/.append style={fill=black}},
    {loosely dashed,green!60!black,every mark/.append style={fill=green!60!black}},
    {densely dashdotted,magenta!90!black,every mark/.append style={fill=magenta!90!black}},
    {densely dashdotdotted,teal,every mark/.append style={fill=teal}},
    {loosely dashdotted,orange,every mark/.append style={fill=orange}},
    {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}

%fill pattern for bar charts similar to the gnuplot one used previously
\pgfplotscreateplotcyclelist{mfill}{
    {fill=white,postaction={pattern=crosshatch,pattern color=red}},
    {fill=white,postaction={pattern=north east lines,pattern color=green}},
    {fill=white,postaction={pattern=north west lines,pattern color=blue}}}

### 2014-02-12 batchdedup/scheduling.tex
paper revision. also major figure refactoring.

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail
distribution, though local minima exist in the histogram and the range of VM
sizes varies.
All of the clusters we have looked at have similarly shaped distributions. Size
distribution histograms for two of the clusters are shown in
Fig.~\ref{fig:hist}. There is a long tail on both histrograms which has been
cut (out to 100GB for the first, and out to 2000GB for the second). The
important thing to get from this data is that in none of the productions
clusters we evaluated was the VM Size distribution flat, which motivates the
importance of round scheduling.

@@

When a multi-round schedule is deployed, the backup of a  VM can be executed in one of these rounds.
Tasks at each round go through the processing stages discussed in Section~\ref{processingStage}.
\begin{figure}[thb]
\centering
\includegraphics[width=0.5\textwidth]{images/VMRound.pdf}
\caption{Choosing a round to schedule a VM (marked as VM1D in a two-round schedule.  }
\label{fig:VMRound}
\end{figure}

>>>>

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail
distribution, though local minima exist in the histogram and the range of VM
sizes varies.
All of the clusters we have looked at have similarly shaped distributions. Size
distribution histograms for two of the clusters are shown in
Fig.~\ref{fig:hist}. Note that there is a long tail on both histrograms which has been
cut (out to 100GB for the first, and out to 2000GB for the second). The
key insight from these size distributions is that in all of the productions
clusters we evaluated, the VM Size distribution is highly skewed, which
motivates the importance of round scheduling.

@@

When a multi-round schedule is deployed, the backup of a  VM can be executed in one of these rounds.
Tasks at each round go through the processing stages discussed in Section~\ref{processingStage}.
\begin{figure}[thb]
\centering
%\includegraphics[width=0.5\textwidth]{VMRound}
%implementation of the above figure in pure latex
\input{figures/VMRound}
\caption{Choosing a round to schedule a VM. New VM marked as VM1A.}
\label{fig:VMRound}
\end{figure}
